\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-09 related-work.tex
mute discussion about 1st v 2nd class families

\noindentparagraph{Solutions to the expression problem} abound.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea found in the context of OO programming,
to the context of mechanized proofs.
Families in \Lang are second-class, in that they are not considered
terms by themselves.
Families as modeled in \TT (namely linkages) are first-class and thus more flexible.
The distinction corresponds to class-based vs.\ object-base family
polymorphism as summarized before~\cite{cdnw07-tribe}.

\citet{bac2006} address the expression problem in a functional language,
introducing a language mechanism that allows pattern-matching cases to
be added retroactively in accordance with extensions to variant types.
Our \lsti{FRecursion} and \lsti{FInduction} commands achieve a similar
functionality, with families bestowing additional organizational power.

>>>>

\noindentparagraph{Solutions to the expression problem} abound.
Almost all solutions involve some form of either explicit or implicit parameterization.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea found in the context of OO programming,
to the context of mechanized proofs.
%Families in \Lang are second-class, in that they are not considered
%terms by themselves.
%Families as modeled in \TT (namely linkages) are first-class and thus more flexible.\EDJ{A more unified way is to consider Coq's Family (our surface syntax) second class corresponds to Inheritance Judgement/Linkage Transformer (secondclass in type theory). Linkage transformer is the helper function to construct first class linkage easily. Even non-derived (surface syntax) family can be considered in this way because they are just inheritance on empty family.}
%The distinction corresponds to class-based vs.\ object-base family
%polymorphism as summarized before~\cite{cdnw07-tribe}.

\citet{bac2006} address the expression problem in a functional setting,
introducing a language mechanism that allows pattern-matching cases to
be added retroactively in accordance with extensions to variant types.
Our \lsti{FRecursion} and \lsti{FInduction} commands achieve a similar
functionality, with families bestowing additional organizational power.
